### 2020-02-19 Paper_EV/Paper_EV.tex
Just backup

- Actuator Dynamics (Estimation of the time constant), plot response with estimated constant\\
- Estimation of the control effectiveness parameters G1, G2 for inner INDI (describe performed flight to log data), plot the curve with contribution of G1, G2 to the fitting\\
- PD gain tuning for inner INDI (using pd\_inner\_cs(), show plots with different D-gains (e.g 25, 10 and 3) to see different damping behaviour), Before explaining gain tuning present all relevant transfer functions of the closed and open loops\\
- Outer loop (show new diagram of the controller)

>>>>

- Actuator Dynamics (Estimation of the time constant), plot response with estimated constant\\
- Thrust dynamics estimation\\
- Estimation of the control effectiveness parameters G1, G2 for inner INDI (describe performed flight to log data), plot the curve with contribution of G1, G2 to the fitting\\
- PD gain tuning for inner INDI (using pd\_inner\_cs(), show plots with different D-gains (e.g 25, 10 and 3) to see different damping behaviour), Before explaining gain tuning present all relevant transfer functions of the closed and open loops\\
- Outer loop (show new diagram of the controller)
